%% start of file `coverletter.tex'.
%% Copyright 2014 Francois Mouton (moutonf@gmail.com).
%
% This template is adapted from the work performed by Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

%example:
% \recipient{Company Recruitment team}{Company, Inc.\\123 somestreet\\some city}
% \date{January 01, 1984}
% \opening{Dear Sir or Madam,}
% \closing{Yours faithfully,}
% \enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine %\enclname
% \makelettertitle
%
% Lorem ipsum dolor sit amet, consectetur adipiscing elit. Duis ullamcorper neque sit amet lectus facilisis sed luctus nisl iaculis. Vivamus at neque arcu, sed tempor quam. Curabitur pharetra tincidunt tincidunt. Morbi volutpat feugiat mauris, quis tempor neque vehicula volutpat. Duis tristique justo vel massa fermentum accumsan. Mauris ante elit, feugiat vestibulum tempor eget, eleifend ac ipsum. Donec scelerisque lobortis ipsum eu vestibulum. Pellentesque vel massa at felis accumsan rhoncus.
% 
% Suspendisse commodo, massa eu congue tincidunt, elit mauris pellentesque orci, cursus tempor odio nisl euismod augue. Aliquam adipiscing nibh ut odio sodales et pulvinar tortor laoreet. Mauris a accumsan ligula. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos. Suspendisse vulputate sem vehicula ipsum varius nec tempus dui dapibus. Phasellus et est urna, ut auctor erat. Sed tincidunt odio id odio aliquam mattis. Donec sapien nulla, feugiat eget adipiscing sit amet, lacinia ut dolor. Phasellus tincidunt, leo a fringilla consectetur, felis diam aliquam urna, vitae aliquet lectus orci nec velit. Vivamus dapibus varius blandit.
% 
% Duis sit amet magna ante, at sodales diam. Aenean consectetur porta risus et sagittis. Ut interdum, enim varius pellentesque tincidunt, magna libero sodales tortor, ut fermentum nunc metus a ante. Vivamus odio leo, tincidunt eu luctus ut, sollicitudin sit amet metus. Nunc sed orci lectus. Ut sodales magna sed velit volutpat sit amet pulvinar diam venenatis.
%
% Albert Einstein discovered that $e=mc^2$ in 1905.
%
% \[ e=\lim_{n \to \infty} \left(1+\frac{1}{n}\right)^n \]
%
% \makeletterclosing
%
% \clearpage



\recipient{To whom it may concern}{}
\date{\today}
\opening{Dear Sir or Madam,}
\closing{Yours faithfully,}
\enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname

\makelettertitle

I would like to take this opportunity to introduce myself, \textbf{Francois Mouton}.

I obtained my BSc Computer Science degree from the University of Pretoria in 2007. As part of this BSc Computer Science degree I also completed all the financial accounting subjects as required for a Bcom degree in order to have a sufficient accounting background. In 2008 I obtained my BSc Computer Science (Honours) degree and in 2012 I obtained my MSc Computer Science degree with distinction also at the University of Pretoria. Along with my MSc Computer Science degree, I also completed all of the undergraduate BA Psychology and Research subjects in order to form a basis for my PhD research in Social Engineering. I also attended an A+ Technician Course from Damelin College in 2004. Currently I am studying towards my PhD Computer Science degree.

During my student years I was employed by the University of Pretoria as an assistant lecturer for undergraduate and postgraduate courses in: Digital Forensics, Computer Security, Computer Networks and Databases.

I was previously employed as an administrator and developer at Abacus Recruitment. I also performed work for Shaya and Cyanre as a digital forensic investigator on a contractual basis. I started working at the CSIR in November, 2011. 

I am part of the Information and Computer Security Architecture research group at the University of Pretoria. At this research group I performed extensive research on security, network attacks and digital forensic readiness in a wireless sensor network domain. I am also supervising MSc and honours students at the University of Pretoria within the field of Social Engineering.

I am currently still employed at the CSIR (Council for Scientific and Industrial Research), in the operating unit of Defence Peace, Safety and Security under the Command, Control and Information Warfare competency area. I am a principle developer on several projects on cyber security, digital forensics and mobile security for the South African defence force.

\makeletterclosing

\clearpage

%% end of file `coverletter.tex'.